---
title: "DETECTR 051 SpectraMax DETECTR and NANCI UMP Data"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
library(dplyr)
library(data.table)
library(ggplot2)
```


```{r include=FALSE}
ggplotRegression <- function (fit) {

require(ggplot2)

ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5)))
}
```

```{r include=FALSE}

convertAMP <- function (fit, value) {

intercept = signif(fit$coef[[1]],5 )
slope = signif(fit$coef[[2]], 5)
AMP = (value - intercept)/slope


return(AMP)
}
```

```{r include=FALSE}
sumBelowTime <- function (DETECTR_037, hour) {

DETECTR_037 = subset(DETECTR_037, (hours < hour) | (hours == hour & minutes == 0 & seconds == 0))
DETECTR_037_sum = DETECTR_037 %>% group_by(standard_conc, replicate) %>% summarize (total_rfu=sum(rfu_value))
return(DETECTR_037_sum)
}
```

## UMP NEBuffer 4 + 2.1 Fresh Standard Curves for concentrations from 0.01uM to 10uM, including 0uM
+ 0hr and 1hr single time points are first two plots
+ Summation of all data points below 1hr and 11hr are the last two plots

### Conclusion 
As before, summing seems to improve the data points and brings them towards the mean. 1hr sum is better than 0hr or 1hr timepoint and 11hr sum is better than 1hr sum.

```{r echo=FALSE}

DETECTR_051 <- read.csv("../tidy_data/DETECTR_051_tidy_metadata.csv")
standard_051 <- subset(DETECTR_051, !(is.na(DETECTR_051$standard_conc)) & DETECTR_051$sample_set == "NANCI_UMP_standard")
standard_051$standard_conc <- as.numeric(as.character(standard_051$standard_conc))

standard_051_0hr_single_point = subset(standard_051,time =="00:00:00")
standard_051_1hr_single_point = subset(standard_051,time =="01:00:00")

standard_051_1hr = sumBelowTime(standard_051,1)
standard_051_11hr = sumBelowTime(standard_051,11)

ggplotRegression(lm(standard_051_0hr_single_point$rfu_value~standard_051_0hr_single_point$standard_conc))
ggplotRegression(lm(standard_051_1hr_single_point$rfu_value~standard_051_1hr_single_point$standard_conc))
ggplotRegression(lm(standard_051_1hr$total_rfu~standard_051_1hr$standard_conc)) 
ggplotRegression(lm(standard_051_11hr$total_rfu~standard_051_11hr$standard_conc)) 


```

## UMP NEBuffer 4+ 2.1 Fresh Standard Curves for concentrations from 0.01uM to 0.16uM, including 0uM
+ 0hr and 1hr single time points are first two plots
+ Summation of all data points below 1hr and 11hr are the last two plots

### Conclusion 
Same as before - summing reduces noise quite a bit. Can detect down to 0.02 uM with summing of just 1hr.

```{r echo=FALSE}

DETECTR_051 <- read.csv("../tidy_data/DETECTR_051_tidy_metadata.csv")
standard_051 <- subset(DETECTR_051, !(is.na(DETECTR_051$standard_conc)) & DETECTR_051$sample_set == "NANCI_UMP_standard")
standard_051$standard_conc <- as.numeric(as.character(standard_051$standard_conc))
standard_051 = subset(standard_051,standard_conc<=0.2)

standard_051_0hr_single_point = subset(standard_051,time =="00:00:00")
standard_051_1hr_single_point = subset(standard_051,time =="01:00:00")
standard_051_1hr = sumBelowTime(standard_051,1)
standard_051_11hr = sumBelowTime(standard_051,11)


ggplotRegression(lm(standard_051_0hr_single_point$rfu_value~standard_051_0hr_single_point$standard_conc))
ggplotRegression(lm(standard_051_1hr_single_point$rfu_value~standard_051_1hr_single_point$standard_conc))
ggplotRegression(lm(standard_051_1hr$total_rfu~standard_051_1hr$standard_conc)) 
ggplotRegression(lm(standard_051_11hr$total_rfu~standard_051_11hr$standard_conc)) 


```

## NANCI UMP
+ Used IDT cas12a and alt-R synthetic IS1081 gRNA with synthetic targets for all
+ The reporter was r17U-TTATT-phos
+ RFU values were converted to UMP uM concentrations using the 1hr summation regression
+ Mismatched target is for IS6110

### Conclusions
2uM of UMP in 10uL is 1.204×10^13 molecules of UMP. Thus, if we assume that the reporter is cleaved in half so roughly 10 UMPs are available, then we are seeing 1.204×10^12 reporters cleaved. This means that 2.4X10^8 molecules of cis cleavage ---> 1.204×10^12 molecules of trans cleavage, or four orders of magnitude of amplification from cas12a activity.

```{r echo=FALSE}
DETECTR_051 <- read.csv("../tidy_data/DETECTR_051_tidy_metadata.csv")
samples_051_UMP <- subset(DETECTR_051, (DETECTR_051$kit=="NANCI_UMP") & !(is.na(DETECTR_051$gRNA))  & !(DETECTR_051$gRNA=="") )
samples_051_UMP = subset(samples_051_UMP, (hours < 1) | (hours == 1 & minutes == 0 & seconds == 0))

samples_051_UMP = samples_051_UMP %>% group_by(gRNA, reporter, target_DNA, target_DNA_input_concentration, target_DNA_input_molecules, sample_set, replicate, kit) %>% summarize (total_rfu=sum(rfu_value))

t.test(subset(samples_051_UMP,target_DNA_input_molecules %in% c(0,2.4e7))$total_rfu~subset(samples_051_UMP,target_DNA_input_molecules %in%  c(0,2.4e7))$target_DNA_input_molecules)

t.test(subset(samples_051_UMP,target_DNA_input_molecules %in% c(0,2.4e8))$total_rfu~subset(samples_051_UMP,target_DNA_input_molecules %in%  c(0,2.4e8))$target_DNA_input_molecules)

standard_051_UMP <- subset(DETECTR_051, !(is.na(DETECTR_051$standard_conc)) & DETECTR_051$sample_set == "NANCI_UMP_standard")

standard_051_UMP_1hr = sumBelowTime(standard_051_UMP,1)

standard_051_UMP_1hr$standard_conc <- as.numeric(as.character(standard_051_UMP_1hr$standard_conc))

samples_051_UMP$UMP <- convertAMP(lm(standard_051_UMP_1hr$total_rfu~standard_051_UMP_1hr$standard_conc), samples_051_UMP$total_rfu)

samples_051_UMP <- samples_051_UMP %>% group_by(gRNA, reporter, target_DNA, target_DNA_input_concentration, target_DNA_input_molecules,sample_set, kit) %>% summarize (mean_rfu_value = mean(total_rfu), sd_rfu_value = sd(total_rfu), mean_amp = mean(UMP), sd_amp = sd(UMP))

samples_051_UMP$sample_name <- factor(c(format(samples_051_UMP$target_DNA_input_molecules[1:10], scientific = TRUE)
, "mismatched_target", "no_gRNA"), levels = c("no_gRNA", "mismatched_target", "0.0e+00","2.4e+04", "2.4e+05","2.4e+06","2.4e+07","2.4e+08","2.4e+09","2.4e+10","2.4e+11","2.4e+12"))

samples_051_UMP$sample_group <- c(replicate(10,"matched_target"), "mismatched_target", "no_gRNA")

ggplot(samples_051_UMP, aes(x = sample_name, y = mean_amp, fill = sample_group)) +
  #facet_wrap(~gRNA)+
  geom_bar(stat = 'identity', position = 'dodge', color = "black") +
  geom_errorbar(aes(ymin=mean_amp-sd_amp, ymax=mean_amp+sd_amp), width=.2,
                 position=position_dodge(.9)) +
  scale_y_continuous(expand = c(0,0), breaks = seq(0,20,1),
                     limits = c(0,20))+
  ggtitle("DETECTR 051, NANCI UMP GLO")+
  scale_fill_manual(values = c("darkslategray3", "mediumpurple3","darkseagreen3","olivedrab4"))+
  scale_x_discrete(labels = function(x) format(x, scientific = TRUE))+
  ylab("average UMP (uM)") +
  #xlab("reporter used")+
  theme(axis.text.x = element_text(angle = 60, hjust = 1), 
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey"),
        panel.border = element_rect(fill = NA, color = "black"),
        title = element_text(face = "bold"),
        strip.background = element_rect(fill = NA, color = "black"),
        strip.text = element_text(size = 10),
        legend.title = element_blank(),
        axis.title.x = element_blank()
)


ggplot(subset(samples_051_UMP,(target_DNA_input_molecules < 5E7) | (target_DNA == "IS6110_A7") | (gRNA == "no_gRNA")), aes(x = sample_name, y = mean_amp, fill = sample_group)) +
  #facet_wrap(~gRNA)+
  geom_bar(stat = 'identity', position = 'dodge', color = "black") +
  geom_errorbar(aes(ymin=mean_amp-sd_amp, ymax=mean_amp+sd_amp), width=.2,
                 position=position_dodge(.9)) +
  scale_y_continuous(expand = c(0,0), breaks = seq(0,20,0.25),
                     limits = c(0,0.5))+
  ggtitle("DETECTR 051, NANCI UMP GLO, low concentrations")+
  scale_fill_manual(values = c("darkslategray3", "mediumpurple3","darkseagreen3","olivedrab4"))+
  scale_x_discrete(labels = function(x) format(x, scientific = TRUE))+
  ylab("average UMP (uM)") +
  #xlab("reporter used")+
  theme(axis.text.x = element_text(angle = 60, hjust = 1), 
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey"),
        panel.border = element_rect(fill = NA, color = "black"),
        title = element_text(face = "bold"),
        strip.background = element_rect(fill = NA, color = "black"),
        strip.text = element_text(size = 10),
        legend.title = element_blank(),
        axis.title.x = element_blank()
)



```

## DETECTR
+ Used IDT cas12a and alt-R synthetic IS1081 gRNA with synthetic targets for all
+ The reporter was FAM-TTATT-IowaBlk
+ RFU values were a sum of all points up to 1hr
+ Background is reporter MM + water (no cas12a, gRNA, etc)
+ Mismatched target is for IS6110

```{r echo=FALSE}
DETECTR_051 <- read.csv("../tidy_data/DETECTR_051_tidy_metadata.csv")
samples_051 <- subset(DETECTR_051, (DETECTR_051$kit=="DETECTR"))

samples_051 = subset(samples_051, (hours < 1) | (hours == 1 & minutes == 0 & seconds == 0))

samples_051 = samples_051 %>% group_by(gRNA, reporter, target_DNA, target_DNA_input_concentration, target_DNA_input_molecules,sample_set, kit, replicate) %>% summarize (total_rfu=sum(rfu_value))


t.test(subset(samples_051,target_DNA_input_molecules %in% c(0,2.4e7))$total_rfu~subset(samples_051,target_DNA_input_molecules %in%  c(0,2.4e7))$target_DNA_input_molecules)

t.test(subset(samples_051,target_DNA_input_molecules %in% c(0,2.4e8))$total_rfu~subset(samples_051,target_DNA_input_molecules %in%  c(0,2.4e8))$target_DNA_input_molecules)


samples_051 <- samples_051 %>% group_by(gRNA, reporter, target_DNA, target_DNA_input_concentration, target_DNA_input_molecules,sample_set, kit) %>% summarize (mean_rfu_value = mean(total_rfu), sd_rfu_value = sd(total_rfu))
samples_051$sample_name <- 
  factor(c("background",format(samples_051$target_DNA_input_molecules[2:11], scientific = TRUE), "mismatched_target", "no_gRNA"),
         levels = c("background", "no_gRNA", "mismatched_target", "0.0e+00","2.4e+04", "2.4e+05","2.4e+06","2.4e+07","2.4e+08","2.4e+09","2.4e+10","2.4e+11","2.4e+12"))

samples_051$sample_group <- c("background",replicate(10,"matched_target"), "mismatched_target", "no_gRNA")


ggplot(samples_051, aes(x = sample_name, y = mean_rfu_value, fill = sample_group)) +
  #facet_wrap(~gRNA)+
  geom_bar(stat = 'identity', position = 'dodge', color = "black") +
  geom_errorbar(aes(ymin=mean_rfu_value-sd_rfu_value, ymax=mean_rfu_value+sd_rfu_value), width=.2,
                 position=position_dodge(.9), color = "black") +
  scale_y_continuous(expand = c(0,0))+
  ggtitle("DETECTR 051, DNA-FAM")+
  scale_fill_manual(values = c("coral2", "goldenrod2","hotpink3", "seagreen3"
                              ))+
  ylab("average rfu value") +
  #xlab("reporter used")+
  theme(axis.text.x = element_text(angle = 60, hjust = 1), 
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey"),
        panel.border = element_rect(fill = NA, color = "black"),
        title = element_text(face = "bold"),
        strip.background = element_rect(fill = NA, color = "black"),
        strip.text = element_text(size = 10),
        legend.title = element_blank(),
        axis.title.x = element_blank()
          
        
)

ggplot(subset(samples_051, (target_DNA_input_molecules<5E7) | (target_DNA == "IS6110_A7") | (gRNA == "no_gRNA") | (sample_name == "background")), 
       aes(x = sample_name, y = mean_rfu_value, fill = sample_group)) +
  geom_bar(stat = 'identity', position = 'dodge', color = "black") +
  geom_errorbar(aes(ymin=mean_rfu_value-sd_rfu_value, ymax=mean_rfu_value+sd_rfu_value), width=.2,
                 position=position_dodge(.9), color = "black") +
  scale_y_continuous(expand = c(0,0))+
  ggtitle("DETECTR 051, DNA-FAM, low concentrations")+
  scale_fill_manual(values = c("coral2", "goldenrod2","hotpink3", "seagreen3"
                              ))+
  ylab("average rfu value") +
  #xlab("reporter used")+
  theme(axis.text.x = element_text(angle = 60, hjust = 1), 
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey"),
        panel.border = element_rect(fill = NA, color = "black"),
        title = element_text(face = "bold"),
        strip.background = element_rect(fill = NA, color = "black"),
        strip.text = element_text(size = 10),
        legend.title = element_blank(),
        axis.title.x = element_blank()
          
        
)


```


## Kinetics

```{r echo=FALSE, warning=FALSE}

DETECTR_051 <- read.csv("../tidy_data/DETECTR_051_tidy_metadata.csv")
DETECTR_051$standard_conc <- as.numeric(as.character(DETECTR_051$standard_conc))
DETECTR_051 <- subset(DETECTR_051,  DETECTR_051$sample_set %in% c("NANCI_UMP_standard") )
DETECTR_051$standard_conc <- factor(DETECTR_051$standard_conc)

ggplot(DETECTR_051, aes(x = time, y = rfu_value, color = standard_conc)) +
  facet_wrap(~sample_set, scale = "free_y")+
  #geom_line(stat = 'identity') +
  geom_point(stat = 'identity', size = 0.5) +
  scale_y_continuous(expand = c(0,0))+
 # scale_x_continuous(breaks = seq(0,24,2))+
  scale_color_manual(name = "concentration (uM)",values = c("darkslategray3", "mediumpurple3","darkseagreen3","olivedrab4","orange","yellow","blue","red","green","brown","black","purple","olivedrab2","grey","pink","orchid3"))+
  ylab("rfu_value") +
  xlab("time from 0 hr to 11 hr")+
  theme(axis.text.x = element_blank(), 
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey"),
        panel.border = element_rect(fill = NA, color = "black"),
        title = element_text(face = "bold"),
        strip.background = element_rect(fill = NA, color = "black"),
        strip.text = element_text(size = 10)
          
        
)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
DETECTR_051 <- read.csv("../tidy_data/DETECTR_051_tidy_metadata.csv")
DETECTR_051$standard_conc <- as.numeric(as.character(DETECTR_051$standard_conc))
DETECTR_051 <- subset(DETECTR_051,  DETECTR_051$sample_set %in% c("NANCI_UMP_sample") )
DETECTR_051$standard_conc <- factor(DETECTR_051$standard_conc)

ggplot(DETECTR_051, aes(x = time, y = rfu_value, color = factor(target_DNA_input_molecules))) +
  facet_wrap(~sample_set, scale = "free_y")+
  #geom_line(stat = 'identity') +
  geom_point(stat = 'identity', size = 0.5) +
  scale_y_continuous(expand = c(0,0))+
 # scale_x_continuous(breaks = seq(0,24,2))+
  scale_color_manual(name = "target DNA (molecules)",values = c("darkslategray3", "mediumpurple3","darkseagreen3","olivedrab4","orange","yellow","blue","red","green","brown","black","purple","olivedrab2","grey","pink","orchid3"))+
  ylab("rfu_value") +
  xlab("time from 0 hr to 11 hr")+
  theme(axis.text.x = element_blank(), 
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey"),
        panel.border = element_rect(fill = NA, color = "black"),
        title = element_text(face = "bold"),
        strip.background = element_rect(fill = NA, color = "black"),
        strip.text = element_text(size = 10)
          
        
)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
DETECTR_051 <- read.csv("../tidy_data/DETECTR_051_tidy_metadata.csv")
DETECTR_051$standard_conc <- as.numeric(as.character(DETECTR_051$standard_conc))
DETECTR_051 <- subset(DETECTR_051,  DETECTR_051$sample_set %in% c("DETECTR_sample") )
DETECTR_051$standard_conc <- factor(DETECTR_051$standard_conc)

ggplot(DETECTR_051, aes(x = time, y = rfu_value, color = factor(format(target_DNA_input_molecules, scientific = TRUE)))) +
  facet_wrap(~sample_set, scale = "free_y")+
  #geom_line(stat = 'identity') +
  geom_point(stat = 'identity', size = 0.5) +
  scale_y_continuous(expand = c(0,0))+
 # scale_x_continuous(breaks = seq(0,24,2))+
  scale_color_manual(name = "target DNA (molecules)",values = c("darkslategray3", "mediumpurple3","darkseagreen3","olivedrab4","orange","yellow","blue","red","green","brown","black","purple","olivedrab2","grey","pink","orchid3"))+
  ylab("rfu_value") +
  xlab("time from 0 hr to 4 hr")+
  theme(axis.text.x = element_blank(), 
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey"),
        panel.border = element_rect(fill = NA, color = "black"),
        title = element_text(face = "bold"),
        strip.background = element_rect(fill = NA, color = "black"),
        strip.text = element_text(size = 10)
          
        
)
```

