---
title: "DETECTR 046 AMP GLO w/o Reagent 1 and w/ larger volumes"
output:
  html_document:
    df_print: paged
---

Main takeaways: Reagent 1 is necessary for sensitive luciferase reaction. However  a small level of luminescence is visible in a concentration dependent manner without it. Larger volume reactions seem to be more sensitive and give larger signal than smaller volumes - this is likely due to more molecules (in retrospect, I should have done the same molecules in a smaller volume...).

```{r setup, include=FALSE}
library(dplyr)
library(data.table)
library(ggplot2)
```


```{r include=FALSE}
ggplotRegression <- function (fit) {

require(ggplot2)

ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5)))
}
```

```{r include=FALSE}

convertAMP <- function (fit, value) {

intercept = signif(fit$coef[[1]],5 )
slope = signif(fit$coef[[2]], 5)
AMP = (value - intercept)/slope


return(AMP)
}
```

```{r include=FALSE}
sumBelowTime <- function (DETECTR_037, hour) {

DETECTR_037 = subset(DETECTR_037, (hours < hour) | (hours == hour & minutes == 0 & seconds == 0))
DETECTR_037_sum = DETECTR_037 %>% group_by(standard_conc, replicate, sample_set) %>% summarize (total_rfu=sum(rfu_value))
return(DETECTR_037_sum)
}
```

# Reagent 1 Test
This experiment was to test if Reagent 1 was necessary for the luciferase reaction. Reagent 1 was replaced with NEBuffer 2.1. Duplicates were performed.

## AMP NEBuffer 4 + 2.1 Thawed Standard Curves for concentrations from 0.01uM to 10uM, including 0uM
+ 0hr and 1hr single time points are first two plots
+ Summation of all data points below 1hr is next plot
+ 1.5 second integration time
+ Used DETECTR_042 no ATP AMP standards

### Conclusion 
The R2 on these look worse than usual.

```{r echo=FALSE}

DETECTR_046 <- read.csv("../tidy_data/DETECTR_046_Reagent1_tidy_metadata.csv")
standard_046 <- subset(DETECTR_046, !(is.na(DETECTR_046$standard_conc)) & DETECTR_046$sample_set == "Reagent1")
standard_046$standard_conc <- as.numeric(as.character(standard_046$standard_conc))

standard_046_0hr_single_point = subset(standard_046,time =="00:00:00")
standard_046_1hr_single_point = subset(standard_046,time =="01:00:00")
#standard_046_30min = sumBelowTime(standard_046,0,30,0)

standard_046_1hr = sumBelowTime(standard_046,1)

ggplotRegression(lm(standard_046_0hr_single_point$rfu_value~standard_046_0hr_single_point$standard_conc))
ggplotRegression(lm(standard_046_1hr_single_point$rfu_value~standard_046_1hr_single_point$standard_conc))
#ggplotRegression(lm(standard_046_30min$total_rfu~standard_046_30min$standard_conc))

ggplotRegression(lm(standard_046_1hr$total_rfu~standard_046_1hr$standard_conc)) 

```

## AMP NEBuffer 4+ 2.1 Thawed Standard Curves for concentrations from 0.01uM to 0.625uM, including 0uM
+ 0hr and 1hr single time points are first two plots
+ Summation of all data points below 1hr is next plot
+ 1.5 second integration time
+ Used DETECTR_042 no ATP AMP standards

### Conclusion 
I would trust down to 0.08uM. Summing helps a little, but data is still very noisy.

```{r echo=FALSE}

DETECTR_046 <- read.csv("../tidy_data/DETECTR_046_Reagent1_tidy_metadata.csv")
standard_046 <- subset(DETECTR_046, !(is.na(DETECTR_046$standard_conc)) & DETECTR_046$sample_set == "Reagent1")
standard_046$standard_conc <- as.numeric(as.character(standard_046$standard_conc))
standard_046 = subset(standard_046,standard_conc<=1)

standard_046_0hr_single_point = subset(standard_046,time =="00:00:00")
standard_046_1hr_single_point = subset(standard_046,time =="01:00:00")
#standard_046_30min = sumBelowTime(standard_046,0,30,0)

standard_046_1hr = sumBelowTime(standard_046,1)

ggplotRegression(lm(standard_046_0hr_single_point$rfu_value~standard_046_0hr_single_point$standard_conc))
ggplotRegression(lm(standard_046_1hr_single_point$rfu_value~standard_046_1hr_single_point$standard_conc))
#ggplotRegression(lm(standard_046_30min$total_rfu~standard_046_30min$standard_conc))

ggplotRegression(lm(standard_046_1hr$total_rfu~standard_046_1hr$standard_conc)) 


```


## No Reagent 1 AMP NEBuffer 4 + 2.1 Thawed Standard Curves for concentrations from 0.01uM to 10uM, including 0uM
+ 0hr and 1hr single time points are first two plots
+ Summation of all data points below 1hr is next plot
+ 1.5 second integration time
+ Used DETECTR_042 no ATP AMP standards

### Conclusion 
Looks like luciferase reaction still occurs, but on a much lower level and with less sensitivity. Makes sense as pyruvate kinase will probably have some activity AMP->ADP->ATP but is more efficient at ADP->ATP. Summing helps (usually does in lower regimes, which is what this essentially is)

```{r echo=FALSE}

DETECTR_046 <- read.csv("../tidy_data/DETECTR_046_Reagent1_tidy_metadata.csv")
standard_046 <- subset(DETECTR_046, !(is.na(DETECTR_046$standard_conc)) & DETECTR_046$sample_set == "NEBuffer2.1")
standard_046$standard_conc <- as.numeric(as.character(standard_046$standard_conc))

standard_046_0hr_single_point = subset(standard_046,time =="00:00:00")
standard_046_1hr_single_point = subset(standard_046,time =="01:00:00")
#standard_046_30min = sumBelowTime(standard_046,0,30,0)

standard_046_1hr = sumBelowTime(standard_046,1)

ggplotRegression(lm(standard_046_0hr_single_point$rfu_value~standard_046_0hr_single_point$standard_conc))
ggplotRegression(lm(standard_046_1hr_single_point$rfu_value~standard_046_1hr_single_point$standard_conc))
#ggplotRegression(lm(standard_046_30min$total_rfu~standard_046_30min$standard_conc))

ggplotRegression(lm(standard_046_1hr$total_rfu~standard_046_1hr$standard_conc)) 

```

## No Reagent 1 AMP NEBuffer 4+ 2.1 Thawed Standard Curves for concentrations from 0.01uM to 0.625uM, including 0uM
+ 0hr and 1hr single time points are first two plots
+ Summation of all data points below 1hr is next plot
+ 1.5 second integration time
+ Used DETECTR_042 no ATP AMP standards

### Conclusion 
Lower concentrations are just noisy.

```{r echo=FALSE}

DETECTR_046 <- read.csv("../tidy_data/DETECTR_046_Reagent1_tidy_metadata.csv")
standard_046 <- subset(DETECTR_046, !(is.na(DETECTR_046$standard_conc)) & DETECTR_046$sample_set == "NEBuffer2.1")
standard_046$standard_conc <- as.numeric(as.character(standard_046$standard_conc))
standard_046 = subset(standard_046,standard_conc<=1)

standard_046_0hr_single_point = subset(standard_046,time =="00:00:00")
standard_046_1hr_single_point = subset(standard_046,time =="01:00:00")
#standard_046_30min = sumBelowTime(standard_046,0,30,0)

standard_046_1hr = sumBelowTime(standard_046,1)

ggplotRegression(lm(standard_046_0hr_single_point$rfu_value~standard_046_0hr_single_point$standard_conc))
ggplotRegression(lm(standard_046_1hr_single_point$rfu_value~standard_046_1hr_single_point$standard_conc))
#ggplotRegression(lm(standard_046_30min$total_rfu~standard_046_30min$standard_conc))

ggplotRegression(lm(standard_046_1hr$total_rfu~standard_046_1hr$standard_conc)) 


```




## Comparison of Reagent 1 vs NEBuffer 2.1 AMP Thawed Standard Curves for concentrations from 0.01uM to 10uM, including 0uM
+ Summation of all data points below 1hr is used
+ Used DETECTR_042 no ATP AMP standards

### Conclusion 
Signal is much higher for those with Reagent 1 instead of NEBuffer 2.1

```{r echo=FALSE}

DETECTR_046 <- read.csv("../tidy_data/DETECTR_046_Reagent1_tidy_metadata.csv")
standard_046 <- DETECTR_046
standard_046$standard_conc <- as.numeric(as.character(standard_046$standard_conc))

standard_046_1hr = sumBelowTime(standard_046,1)

ggplot(standard_046_1hr, aes(x = standard_conc, y = total_rfu, color = sample_set)) +
  geom_point(stat = 'identity', size = 1) +
  scale_y_continuous(expand = c(0,0))+
  scale_color_manual(values = c("darkslategray3", "mediumpurple3","darkseagreen3","olivedrab4","orange","yellow","blue","red","green","brown","black","purple","olivedrab2","grey","pink","orchid3"))+
  ylab("rfu_value") +
  xlab("concentration (uM)")+
  ggtitle("AMP Plots")+
  theme(
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey"),
        panel.border = element_rect(fill = NA, color = "black"),
        title = element_text(face = "bold"),
        strip.background = element_rect(fill = NA, color = "black"),
        strip.text = element_text(size = 10),
        legend.title = element_blank())

standard_046_1hr = subset(standard_046_1hr,standard_conc<=1)

ggplot(standard_046_1hr, aes(x = standard_conc, y = total_rfu, color = sample_set)) +
  geom_point(stat = 'identity', size = 1) +
  scale_y_continuous(expand = c(0,0))+
  scale_color_manual(values = c("darkslategray3", "mediumpurple3","darkseagreen3","olivedrab4","orange","yellow","blue","red","green","brown","black","purple","olivedrab2","grey","pink","orchid3"))+
  ylab("rfu_value") +
  xlab("concentration (uM)")+
  ggtitle("AMP Plots, low concentrations")+
  theme(
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey"),
        panel.border = element_rect(fill = NA, color = "black"),
        title = element_text(face = "bold"),
        strip.background = element_rect(fill = NA, color = "black"),
        strip.text = element_text(size = 10),
        legend.title = element_blank())



```


## Kinetics over time
Signal seems to be much lower than usual - 300 rfu? It also looks less stable.

```{r echo=FALSE, warning=FALSE}

DETECTR_046 <- read.csv("../tidy_data/DETECTR_046_Reagent1_tidy_metadata.csv")
DETECTR_046$standard_conc <- as.numeric(as.character(DETECTR_046$standard_conc))
DETECTR_046$standard_conc <- factor(DETECTR_046$standard_conc)

ggplot(DETECTR_046, aes(x = time, y = rfu_value, color = standard_conc)) +
  facet_wrap(~sample_set, scale = "free_y")+
  #geom_line(stat = 'identity') +
  geom_point(stat = 'identity', size = 0.5) +
  scale_y_continuous(expand = c(0,0))+
 # scale_x_continuous(breaks = seq(0,24,2))+
  #scale_color_discrete(face = "concentration(uM)")+
  scale_color_manual(name = "concentration(uM)", values = c("darkslategray3", "mediumpurple3","darkseagreen3","olivedrab4","orange","yellow","blue","red","green","brown","black","purple","olivedrab2","grey","pink","orchid3"))+
  ylab("rfu_value") +
  xlab("time from 0 hr to 1 hr")+
  theme(axis.text.x = element_blank(), 
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey"),
        panel.border = element_rect(fill = NA, color = "black"),
        title = element_text(face = "bold"),
        strip.background = element_rect(fill = NA, color = "black"),
        strip.text = element_text(size = 10)
          
        
)
```



# Larger Volume Test
100uL reaction was compared to 20uL reaction with same input concentration (NOT moles). This was done in a normal volume black/black 384 well plate.


## 20uL AMP NEBuffer 4 + 2.1 Fresh Standard Curves for concentrations from 0.01uM to 10uM, including 0uM
+ 0hr and 1hr single time points are first two plots
+ Summation of all data points below 1hr is next plot
+ 1.5 second integration time

### Conclusion 
I used fresh Kinase and fresh standards for this experiment so the values are a lot higher. 

```{r echo=FALSE}

DETECTR_046 <- read.csv("../tidy_data/DETECTR_046_LargerVolumes_tidy_metadata.csv")
standard_046 <- subset(DETECTR_046, !(is.na(DETECTR_046$standard_conc)) & DETECTR_046$sample_set == "20uL")
standard_046$standard_conc <- as.numeric(as.character(standard_046$standard_conc))

standard_046_0hr_single_point = subset(standard_046,time =="00:00:00")
standard_046_1hr_single_point = subset(standard_046,time =="01:00:00")
#standard_046_30min = sumBelowTime(standard_046,0,30,0)

standard_046_1hr = sumBelowTime(standard_046,1)

ggplotRegression(lm(standard_046_0hr_single_point$rfu_value~standard_046_0hr_single_point$standard_conc))
ggplotRegression(lm(standard_046_1hr_single_point$rfu_value~standard_046_1hr_single_point$standard_conc))
#ggplotRegression(lm(standard_046_30min$total_rfu~standard_046_30min$standard_conc))

ggplotRegression(lm(standard_046_1hr$total_rfu~standard_046_1hr$standard_conc)) 

```


## 20uL AMP NEBuffer 4+ 2.1 Fresh Standard Curves for concentrations from 0.01uM to 0.625uM, including 0uM
+ 0hr and 1hr single time points are first two plots
+ Summation of all data points below 1hr is next plot
+ 1.5 second integration time

### Conclusion 
Noisy below 0.01uM. Hard to make a direct comparison about integration time on this one because the plates are different (black vs white)

```{r echo=FALSE}

DETECTR_046 <- read.csv("../tidy_data/DETECTR_046_LargerVolumes_tidy_metadata.csv")
standard_046 <- subset(DETECTR_046, !(is.na(DETECTR_046$standard_conc)) & DETECTR_046$sample_set == "20uL")
standard_046$standard_conc <- as.numeric(as.character(standard_046$standard_conc))
standard_046 = subset(standard_046,standard_conc<=1)

standard_046_0hr_single_point = subset(standard_046,time =="00:00:00")
standard_046_1hr_single_point = subset(standard_046,time =="01:00:00")
#standard_046_30min = sumBelowTime(standard_046,0,30,0)

standard_046_1hr = sumBelowTime(standard_046,1)

ggplotRegression(lm(standard_046_0hr_single_point$rfu_value~standard_046_0hr_single_point$standard_conc))
ggplotRegression(lm(standard_046_1hr_single_point$rfu_value~standard_046_1hr_single_point$standard_conc))
#ggplotRegression(lm(standard_046_30min$total_rfu~standard_046_30min$standard_conc))

ggplotRegression(lm(standard_046_1hr$total_rfu~standard_046_1hr$standard_conc)) 


```


## 20uL AMP NEBuffer 4+ 2.1 Fresh Standard Curves for concentrations from 0.01uM to 0.08uM, including 0uM
+ 0hr and 1hr single time points are first two plots
+ Summation of all data points below 1hr is next plot
+ 1.5 second integration time

### Conclusion 
For the 20uL volume, I don't trust below 0.08uM. 

```{r echo=FALSE}

DETECTR_046 <- read.csv("../tidy_data/DETECTR_046_LargerVolumes_tidy_metadata.csv")
standard_046 <- subset(DETECTR_046, !(is.na(DETECTR_046$standard_conc)) & DETECTR_046$sample_set == "20uL")
standard_046$standard_conc <- as.numeric(as.character(standard_046$standard_conc))
standard_046 = subset(standard_046,standard_conc<=0.1)

standard_046_0hr_single_point = subset(standard_046,time =="00:00:00")
standard_046_1hr_single_point = subset(standard_046,time =="01:00:00")
#standard_046_30min = sumBelowTime(standard_046,0,30,0)

standard_046_1hr = sumBelowTime(standard_046,1)

ggplotRegression(lm(standard_046_0hr_single_point$rfu_value~standard_046_0hr_single_point$standard_conc))
ggplotRegression(lm(standard_046_1hr_single_point$rfu_value~standard_046_1hr_single_point$standard_conc))
#ggplotRegression(lm(standard_046_30min$total_rfu~standard_046_30min$standard_conc))

ggplotRegression(lm(standard_046_1hr$total_rfu~standard_046_1hr$standard_conc)) 


```

## 100uL AMP NEBuffer 4 + 2.1 Fresh Standard Curves for concentrations from 0.01uM to 10uM, including 0uM
+ 0hr and 1hr single time points are first two plots
+ Summation of all data points below 1hr is next plot
+ 1.5 second integration time

### Conclusion 
The overall regression looks better for the 20uL volume, maybe because the 10uM point was saturated on 100uL. Summing also doesn't seem to help. 

```{r echo=FALSE}

DETECTR_046 <- read.csv("../tidy_data/DETECTR_046_LargerVolumes_tidy_metadata.csv")
standard_046 <- subset(DETECTR_046, !(is.na(DETECTR_046$standard_conc)) & DETECTR_046$sample_set == "100uL")
standard_046$standard_conc <- as.numeric(as.character(standard_046$standard_conc))

standard_046_0hr_single_point = subset(standard_046,time =="00:00:00")
standard_046_1hr_single_point = subset(standard_046,time =="01:00:00")
#standard_046_30min = sumBelowTime(standard_046,0,30,0)

standard_046_1hr = sumBelowTime(standard_046,1)

ggplotRegression(lm(standard_046_0hr_single_point$rfu_value~standard_046_0hr_single_point$standard_conc))
ggplotRegression(lm(standard_046_1hr_single_point$rfu_value~standard_046_1hr_single_point$standard_conc))
#ggplotRegression(lm(standard_046_30min$total_rfu~standard_046_30min$standard_conc))

ggplotRegression(lm(standard_046_1hr$total_rfu~standard_046_1hr$standard_conc)) 

```


## 100uL AMP NEBuffer 4+ 2.1 Fresh Standard Curves for concentrations from 0.01uM to 0.625uM, including 0uM
+ 0hr and 1hr single time points are first two plots
+ Summation of all data points below 1hr is next plot
+ 1.5 second integration time

### Conclusion 
As before with 20uL, non linear in the lower regimes.

```{r echo=FALSE}

DETECTR_046 <- read.csv("../tidy_data/DETECTR_046_LargerVolumes_tidy_metadata.csv")
standard_046 <- subset(DETECTR_046, !(is.na(DETECTR_046$standard_conc)) & DETECTR_046$sample_set == "100uL")
standard_046$standard_conc <- as.numeric(as.character(standard_046$standard_conc))
standard_046 = subset(standard_046,standard_conc<=1)

standard_046_0hr_single_point = subset(standard_046,time =="00:00:00")
standard_046_1hr_single_point = subset(standard_046,time =="01:00:00")
#standard_046_30min = sumBelowTime(standard_046,0,30,0)

standard_046_1hr = sumBelowTime(standard_046,1)

ggplotRegression(lm(standard_046_0hr_single_point$rfu_value~standard_046_0hr_single_point$standard_conc))
ggplotRegression(lm(standard_046_1hr_single_point$rfu_value~standard_046_1hr_single_point$standard_conc))
#ggplotRegression(lm(standard_046_30min$total_rfu~standard_046_30min$standard_conc))

ggplotRegression(lm(standard_046_1hr$total_rfu~standard_046_1hr$standard_conc)) 


```



## 100uL AMP NEBuffer 4+ 2.1 Fresh Standard Curves for concentrations from 0.01uM to 0.08uM, including 0uM
+ 0hr and 1hr single time points are first two plots
+ Summation of all data points below 1hr is next plot
+ 1.5 second integration time

### Conclusion 
When zooming in, I would trust down to 0.018uM, which is better than before. This makes sense - 5X the volume would be 5X the molecules, translating to the 4X more concentration sensitivity.

```{r echo=FALSE}

DETECTR_046 <- read.csv("../tidy_data/DETECTR_046_LargerVolumes_tidy_metadata.csv")
standard_046 <- subset(DETECTR_046, !(is.na(DETECTR_046$standard_conc)) & DETECTR_046$sample_set == "100uL")
standard_046$standard_conc <- as.numeric(as.character(standard_046$standard_conc))
standard_046 = subset(standard_046,standard_conc<=0.1)

standard_046_0hr_single_point = subset(standard_046,time =="00:00:00")
standard_046_1hr_single_point = subset(standard_046,time =="01:00:00")
#standard_046_30min = sumBelowTime(standard_046,0,30,0)

standard_046_1hr = sumBelowTime(standard_046,1)

ggplotRegression(lm(standard_046_0hr_single_point$rfu_value~standard_046_0hr_single_point$standard_conc))
ggplotRegression(lm(standard_046_1hr_single_point$rfu_value~standard_046_1hr_single_point$standard_conc))
#ggplotRegression(lm(standard_046_30min$total_rfu~standard_046_30min$standard_conc))

ggplotRegression(lm(standard_046_1hr$total_rfu~standard_046_1hr$standard_conc)) 


```





## 20uL vs 100uL AMP NEBuffer 4 + 2.1 Fresh Standard Curves
+ Single 1hr timepoint is used

### Conclusion 
Illustrates the much higher rfu values for 100uL.

```{r echo=FALSE}

DETECTR_046 <- read.csv("../tidy_data/DETECTR_046_LargerVolumes_tidy_metadata.csv")
standard_046 <- DETECTR_046
standard_046$standard_conc <- as.numeric(as.character(standard_046$standard_conc))
standard_046_1hr <- subset(standard_046, time == "01:00:00")

ggplot(standard_046_1hr, aes(x = standard_conc, y = rfu_value, color = sample_set)) +
  geom_point(stat = 'identity', size = 2) +
  scale_y_continuous(expand = c(0,0))+
  scale_color_manual(values = c("darkslategray3", "mediumpurple3","darkseagreen3","olivedrab4","orange","yellow","blue","red","green","brown","black","purple","olivedrab2","grey","pink","orchid3"))+
  ylab("rfu_value") +
  xlab("concentration (uM)")+
  ggtitle("AMP Plots")+
  theme(
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey"),
        panel.border = element_rect(fill = NA, color = "black"),
        title = element_text(face = "bold"),
        strip.background = element_rect(fill = NA, color = "black"),
        strip.text = element_text(size = 10),
        legend.title = element_blank())

standard_046_1hr = subset(standard_046_1hr,standard_conc<=1)

ggplot(standard_046_1hr, aes(x = standard_conc, y = rfu_value, color = sample_set)) +
  geom_point(stat = 'identity', size = 1.5) +
  scale_y_continuous(expand = c(0,0))+
  scale_color_manual(values = c("darkslategray3", "mediumpurple3","darkseagreen3","olivedrab4","orange","yellow","blue","red","green","brown","black","purple","olivedrab2","grey","pink","orchid3"))+
  ylab("rfu_value") +
  xlab("concentration (uM)")+
  ggtitle("AMP Plots, low concentrations")+
  theme(
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey"),
        panel.border = element_rect(fill = NA, color = "black"),
        title = element_text(face = "bold"),
        strip.background = element_rect(fill = NA, color = "black"),
        strip.text = element_text(size = 10),
        legend.title = element_blank())



```



## Kinetics over time
There is an outlier in the 10uM standard. Kinetics look similar. 20uL might be saturating faster.

```{r echo=FALSE, warning=FALSE}

DETECTR_046 <- read.csv("../tidy_data/DETECTR_046_LargerVolumes_tidy_metadata.csv")
DETECTR_046$standard_conc <- as.numeric(as.character(DETECTR_046$standard_conc))
DETECTR_046$standard_conc <- factor(DETECTR_046$standard_conc)

ggplot(DETECTR_046, aes(x = time, y = rfu_value, color = standard_conc)) +
  facet_wrap(~sample_set, scale = "free_y")+
  #geom_line(stat = 'identity') +
  geom_point(stat = 'identity', size = 0.5) +
  scale_y_continuous(expand = c(0,0))+
 # scale_x_continuous(breaks = seq(0,24,2))+
  #scale_color_discrete(face = "concentration(uM)")+
  scale_color_manual(name = "concentration(uM)", values = c("darkslategray3", "mediumpurple3","darkseagreen3","olivedrab4","orange","yellow","blue","red","green","brown","black","purple","olivedrab2","grey","pink","orchid3"))+
  ylab("rfu_value") +
  xlab("time from 0 hr to 1 hr")+
  theme(axis.text.x = element_blank(), 
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey"),
        panel.border = element_rect(fill = NA, color = "black"),
        title = element_text(face = "bold"),
        strip.background = element_rect(fill = NA, color = "black"),
        strip.text = element_text(size = 10)
          
        
)
```