---
title: "DETECTR_041 SpectraMax Data"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
library(dplyr)
library(data.table)
library(ggplot2)
```

```{r include=FALSE}
ggplotRegression <- function (fit) {

require(ggplot2)

ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5)))
}
```

```{r include=FALSE}

convertAMP <- function (fit, value) {

intercept = signif(fit$coef[[1]],5 )
slope = signif(fit$coef[[2]], 5)
AMP = (value - intercept)/slope


return(AMP)
}
```

```{r include=FALSE}
sumBelowTime <- function (DETECTR_037, hour) {

DETECTR_037 = subset(DETECTR_037, (hours < hour) | (hours == hour & minutes == 0 & seconds == 0))
DETECTR_037_sum = DETECTR_037 %>% group_by(standard_conc, replicate) %>% summarize (total_rfu=sum(rfu_value))
return(DETECTR_037_sum)
}
```

## AMP GLO NEBuffer 4 + 2.1 Thawed Standard Curves for concentrations from 0.01uM to 10uM, including 0uM
+ 0hr and 1hr single time points are first two plots
+ Summation of all data points below 1hr, 3hr, 6hr and 12hr are the last four plots
+ Note: used DETECTR 040 standards

### Conclusion 
For all samples, summing up all rfu values that came before a certain timepoint gives no noticeable gains on the R2 value. The 0 timepoint looks worse than the 1 hr timempoint again.

```{r echo=FALSE}

DETECTR_041 <- read.csv("../tidy_data/DETECTR_041_kinetics_tidy_metadata.csv")
standard_041 <- subset(DETECTR_041, DETECTR_041$sample_set == "AMP_standard" & !(is.na(DETECTR_041$time)) & !(is.na(DETECTR_041$rfu_value)))
standard_041$standard_conc <- as.numeric(as.character(standard_041$standard_conc))

standard_041_0hr_single_point = subset(standard_041,time =="00:-10:00")
standard_041_1hr_single_point = subset(standard_041,time =="00:50:00")
#standard_041_30min = sumBelowTime(standard_041,0,30,0)

standard_041_1hr = sumBelowTime(standard_041,1)
standard_041_3hr = sumBelowTime(standard_041,3)
standard_041_6hr = sumBelowTime(standard_041,6)
standard_041_12hr = sumBelowTime(standard_041,12)
ggplotRegression(lm(standard_041_0hr_single_point$rfu_value~standard_041_0hr_single_point$standard_conc))
ggplotRegression(lm(standard_041_1hr_single_point$rfu_value~standard_041_1hr_single_point$standard_conc))
#ggplotRegression(lm(standard_041_30min$total_rfu~standard_041_30min$standard_conc))

ggplotRegression(lm(standard_041_1hr$total_rfu~standard_041_1hr$standard_conc)) 
ggplotRegression(lm(standard_041_3hr$total_rfu~standard_041_3hr$standard_conc))
ggplotRegression(lm(standard_041_6hr$total_rfu~standard_041_6hr$standard_conc))

ggplotRegression(lm(standard_041_12hr$total_rfu~standard_041_12hr$standard_conc))


#standard_041_30min_to_1hr = subset(standard_041, (hours <= 0 & minutes <= 50 & seconds <= 0) & (hours <= 0 & minutes >= 20 & seconds <= 0)) 

#standard_041_30min_to_1hr = standard_041_30min_to_1hr %>% group_by(standard_conc, replicate) %>% summarize (total_rfu=sum(rfu_value))


#ggplotRegression(lm(standard_041_30min_to_1hr$total_rfu~standard_041_30min_to_1hr$standard_conc))


```

```{r}
fit = lm(standard_041_0hr_single_point$rfu_value~standard_041_0hr_single_point$standard_conc)
summary(fit)
```

## UMP GLO NEBuffer 4 + 2.1 Fresh Standard Curves for concentrations from 0.01uM to 10uM, including 0uM
+ 0hr and 1hr single time points are first two plots
+ Summation of all data points below 1hr, 3hr, 6hr and 12hr are the last four plots

### Conclusion 
UMP standard curve looks really good for all samples. Summing gives no noticeable gains on R2 value. 

```{r echo=FALSE}

DETECTR_041 <- read.csv("../tidy_data/DETECTR_041_kinetics_tidy_metadata.csv")
standard_041 <- subset(DETECTR_041, DETECTR_041$sample_set == "UMP_standard" & !(is.na(DETECTR_041$time)) & !(is.na(DETECTR_041$rfu_value)))
standard_041$standard_conc <- as.numeric(as.character(standard_041$standard_conc))

standard_041_0hr_single_point = subset(standard_041,time =="00:-10:00")
standard_041_1hr_single_point = subset(standard_041,time =="00:50:00")
#standard_041_30min = sumBelowTime(standard_041,0,30,0)

standard_041_1hr = sumBelowTime(standard_041,1)
standard_041_3hr = sumBelowTime(standard_041,3)
standard_041_6hr = sumBelowTime(standard_041,6)
standard_041_12hr = sumBelowTime(standard_041,12)
ggplotRegression(lm(standard_041_0hr_single_point$rfu_value~standard_041_0hr_single_point$standard_conc))
ggplotRegression(lm(standard_041_1hr_single_point$rfu_value~standard_041_1hr_single_point$standard_conc))
#ggplotRegression(lm(standard_041_30min$total_rfu~standard_041_30min$standard_conc))

ggplotRegression(lm(standard_041_1hr$total_rfu~standard_041_1hr$standard_conc)) 
ggplotRegression(lm(standard_041_3hr$total_rfu~standard_041_3hr$standard_conc))
ggplotRegression(lm(standard_041_6hr$total_rfu~standard_041_6hr$standard_conc))

ggplotRegression(lm(standard_041_12hr$total_rfu~standard_041_12hr$standard_conc))

#standard_041_30min_to_1hr = subset(standard_041, (hours <= 0 & minutes <= 50 & seconds <= 0) & (hours <= 0 & minutes >= 20 & seconds <= 0)) 

#standard_041_30min_to_1hr = standard_041_30min_to_1hr %>% group_by(standard_conc, replicate) %>% summarize (total_rfu=sum(rfu_value))


#ggplotRegression(lm(standard_041_30min_to_1hr$total_rfu~standard_041_30min_to_1hr$standard_conc))


```

## AMP GLO NEBuffer 4 + 2.1 Thawed Standard Curves for concentrations from 0.01uM to 0.625uM, including 0uM
+ 0hr and 1hr single time points are first two plots
+ Summation of all data points below 1hr, 3hr, 6hr and 12hr are the last four plots
+ Note: used DETECTR 040 standards

### Conclusion 
Low concentrations actually look decent on this batch too. 0 hr timepoint looks worse than 1 hr timepoint, as shown in DETECTR 040. Summing helps a little. I would trust 0.15uM and above.

```{r echo=FALSE}

DETECTR_041 <- read.csv("../tidy_data/DETECTR_041_kinetics_tidy_metadata.csv")
standard_041 <- subset(DETECTR_041, DETECTR_041$sample_set == "AMP_standard" & !(is.na(DETECTR_041$time)) & !(is.na(DETECTR_041$rfu_value)))
standard_041$standard_conc <- as.numeric(as.character(standard_041$standard_conc))
standard_041 = subset(standard_041,standard_conc<=0.625)
standard_041_0hr_single_point = subset(standard_041,time =="00:00:00")
standard_041_1hr_single_point = subset(standard_041,time =="00:50:00")
#standard_041_30min = sumBelowTime(standard_041,0,30,0)

standard_041_1hr = sumBelowTime(standard_041,1)
standard_041_3hr = sumBelowTime(standard_041,3)
standard_041_6hr = sumBelowTime(standard_041,6)
standard_041_12hr = sumBelowTime(standard_041,12)
ggplotRegression(lm(standard_041_0hr_single_point$rfu_value~standard_041_0hr_single_point$standard_conc))
ggplotRegression(lm(standard_041_1hr_single_point$rfu_value~standard_041_1hr_single_point$standard_conc))
#ggplotRegression(lm(standard_041_30min$total_rfu~standard_041_30min$standard_conc))

ggplotRegression(lm(standard_041_1hr$total_rfu~standard_041_1hr$standard_conc)) 
ggplotRegression(lm(standard_041_3hr$total_rfu~standard_041_3hr$standard_conc))
ggplotRegression(lm(standard_041_6hr$total_rfu~standard_041_6hr$standard_conc))

ggplotRegression(lm(standard_041_12hr$total_rfu~standard_041_12hr$standard_conc))


```



## UMP GLO NEBuffer 4+ 2.1 Fresh Standard Curves for concentrations from 0.01uM to 0.625uM, including 0uM

+ 0hr and 1hr single time points are first two plots
+ Summation of all data points below 1hr, 3hr, 6hr and 12hr are the last four plots

### Conclusion 
UMP standard curve lower concentration samples really seem benefit from summing over time. I would trust the 0.04uM point on the 1hr sum. It does seem to get rid of the noise to sum overnight instead of 1hr, might actually be worth it for UMP GLO.

```{r echo=FALSE}

DETECTR_041 <- read.csv("../tidy_data/DETECTR_041_kinetics_tidy_metadata.csv")
standard_041 <- subset(DETECTR_041, DETECTR_041$sample_set == "UMP_standard" & !(is.na(DETECTR_041$time)) & !(is.na(DETECTR_041$rfu_value)))
standard_041$standard_conc <- as.numeric(as.character(standard_041$standard_conc))
standard_041 = subset(standard_041,standard_conc<=0.625)
standard_041_0hr_single_point = subset(standard_041,time =="00:00:00")
standard_041_1hr_single_point = subset(standard_041,time =="00:50:00")
#standard_041_30min = sumBelowTime(standard_041,0,30,0)

standard_041_1hr = sumBelowTime(standard_041,1)
standard_041_3hr = sumBelowTime(standard_041,3)
standard_041_6hr = sumBelowTime(standard_041,6)
standard_041_12hr = sumBelowTime(standard_041,12)
ggplotRegression(lm(standard_041_0hr_single_point$rfu_value~standard_041_0hr_single_point$standard_conc))
ggplotRegression(lm(standard_041_1hr_single_point$rfu_value~standard_041_1hr_single_point$standard_conc))
#ggplotRegression(lm(standard_041_30min$total_rfu~standard_041_30min$standard_conc))

ggplotRegression(lm(standard_041_1hr$total_rfu~standard_041_1hr$standard_conc)) 
ggplotRegression(lm(standard_041_3hr$total_rfu~standard_041_3hr$standard_conc))
ggplotRegression(lm(standard_041_6hr$total_rfu~standard_041_6hr$standard_conc))

ggplotRegression(lm(standard_041_12hr$total_rfu~standard_041_12hr$standard_conc))

#standard_041_30min_to_1hr = subset(standard_041, (hours <= 0 & minutes <= 50 & seconds <= 0) & (hours <= 0 & minutes >= 20 & seconds <= 0)) 

#standard_041_30min_to_1hr = standard_041_30min_to_1hr %>% group_by(standard_conc, replicate) %>% summarize (total_rfu=sum(rfu_value))


#ggplotRegression(lm(standard_041_30min_to_1hr$total_rfu~standard_041_30min_to_1hr$standard_conc))
```


## AMP 0uM standards in row below AMP standard curve starting at 10uM and going down to 0uM
The AMP standards were in rows A, C and E for this plate. I placed 0uM standards in rows B, D, and F.

### Conclusions
There seems to be a noticeable trend in higher values in the left columns, where the higher conc standards are. However, it is not completely outside of the expected variance. Some of the right column 0uM wells still reach fairly high values. We can conclude that there is probably a little crosstalk from the high concentration standards, but probably wouldn't make a negative sample appear positive.

```{r echo=FALSE}
#DETECTR_041$AMP <- convertAMP(lm(standard_041$rfu_value~standard_041$standard_conc), DETECTR_041$rfu_value)
DETECTR_041 <- read.csv("../tidy_data/DETECTR_041_kinetics_tidy_metadata.csv")

samples_040 <- subset(DETECTR_041, DETECTR_041$time=="00:50:00" & DETECTR_041$sample_set=="AMP_0_proximal" )

#samples_040 <- samples_040 %>% group_by(gRNA, reporter, target) %>% summarize (mean_rfu_value = mean(rfu_value), sd_rfu_value = sd(rfu_value), mean_amp = mean(AMP), sd_amp = sd(AMP))

ggplot(samples_040, aes(x = column_384, y = rfu_value, color = row_384)) +
  geom_line(stat = 'identity') +
  scale_y_continuous(expand = c(0,0))+
  ggtitle("DETECTR 041, 0 uM AMP proximal to AMP standard curve")+
  scale_color_manual(values = c("darkslategray3", "mediumpurple3","darkseagreen3","olivedrab4"))+
  ylab("rfu_value") +
  xlab("row")+
  scale_x_continuous(breaks = seq(0,24,2))+
  geom_point(stat = 'identity') +
  theme(axis.text.x = element_text(angle = 60, hjust = 1), 
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey"),
        panel.border = element_rect(fill = NA, color = "black"),
        title = element_text(face = "bold"),
        strip.background = element_rect(fill = NA, color = "black"),
        strip.text = element_text(size = 10),
        legend.title = element_blank()
          
        
)
```



## Water in row below UMP standard curve starting at 10uM and going down to 0uM
The UMP standards were in rows H, J and L for this plate. I pulled the waters directly below them in rows I, K and M.

### Conclusions
There is no noticeable cross-talk from the UMP standards to the adjacent waters.

```{r echo=FALSE}
#DETECTR_041$AMP <- convertAMP(lm(standard_041$rfu_value~standard_041$standard_conc), DETECTR_041$rfu_value)
DETECTR_041 <- read.csv("../tidy_data/DETECTR_041_kinetics_tidy_metadata.csv")

samples_040 <- subset(DETECTR_041, DETECTR_041$time=="00:50:00" & DETECTR_041$sample_set=="UMP_water_proximal" )

#samples_040 <- samples_040 %>% group_by(gRNA, reporter, target) %>% summarize (mean_rfu_value = mean(rfu_value), sd_rfu_value = sd(rfu_value), mean_amp = mean(AMP), sd_amp = sd(AMP))

ggplot(samples_040, aes(x = column_384, y = rfu_value, color = row_384)) +
  geom_line(stat = 'identity') +
  scale_y_continuous(expand = c(0,0))+
  scale_x_continuous(breaks = seq(0,24,2))+
  geom_point(stat = 'identity') +
  ggtitle("DETECTR 041, water proximal to UMP standard curve")+
  scale_color_manual(values = c("darkslategray3", "mediumpurple3","darkseagreen3","olivedrab4"))+
  ylab("rfu_value") +
  xlab("row")+
  theme(axis.text.x = element_text(angle = 60, hjust = 1), 
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey"),
        panel.border = element_rect(fill = NA, color = "black"),
        title = element_text(face = "bold"),
        strip.background = element_rect(fill = NA, color = "black"),
        strip.text = element_text(size = 10),
        legend.title = element_blank()
          
        
)
```



## Comparing proximal and distal AMP 0uM standards and proximal water wells
The AMP standards were in rows A, C and E for this plate. I placed 0uM AMP standards in rows B, D, and F.
The UMP standards were in rows H, J and L for this plate. I pulled the waters directly below them in rows I, K and M.
The distal 0uM AMP standards were in row N, O and P on the plate.

### Conclusions
Proximal 0uM AMP standards to the 10uM and 5uM have slightly higher signal than those in the distal category. However, majority of signal is coming from the reagent itself, which you can see by comparing to water wells.

```{r echo=FALSE}
#DETECTR_041$AMP <- convertAMP(lm(standard_041$rfu_value~standard_041$standard_conc), DETECTR_041$rfu_value)
DETECTR_041 <- read.csv("../tidy_data/DETECTR_041_kinetics_tidy_metadata.csv")

samples_040 <- subset(DETECTR_041, DETECTR_041$time=="00:50:00" & DETECTR_041$sample_set %in% c("UMP_water_proximal", "AMP_0_proximal","AMP_0_distal"))

#samples_040 <- samples_040 %>% group_by(gRNA, reporter, target) %>% summarize (mean_rfu_value = mean(rfu_value), sd_rfu_value = sd(rfu_value), mean_amp = mean(AMP), sd_amp = sd(AMP))

ggplot(samples_040, aes(x = column_384, y = rfu_value, color = row_384)) +
  facet_wrap(~sample_set)+
  geom_line(stat = 'identity') +
  scale_y_continuous(expand = c(0,0))+
  scale_x_continuous(breaks = seq(0,24,2))+
  geom_point(stat = 'identity') +
  ggtitle("DETECTR 041\n0uM AMP standard and waters proximal and distal from standard curves")+
  scale_color_manual(values = c("darkslategray3", "mediumpurple3","darkseagreen3","olivedrab4","orange","yellow","blue","red","green"))+
  ylab("rfu_value") +
  xlab("row")+
  theme(axis.text.x = element_text(angle = 60, hjust = 1), 
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey"),
        panel.border = element_rect(fill = NA, color = "black"),
        title = element_text(face = "bold"),
        strip.background = element_rect(fill = NA, color = "black"),
        strip.text = element_text(size = 10),
        legend.title = element_blank()
          
        
)
```

## Comparing all water wells on the plate
The AMP standards were in rows A, C and E for this plate, in odd columns. The UMP standards were in rows H, J and L for this plate, in odd columns. The distal 0uM AMP standards were in row N, O and P on the plate, in odd columns.

### Conclusions
Waters next to the 10uM and 5uM have higher signal than those farther away. None of that signal is higher than a 0 uM AMP standard (~750). There is more cross-talk in directly adjacent cells than in diagonal wells, and if the well is near more than 1 high signal well.

```{r echo=FALSE}
#DETECTR_041$AMP <- convertAMP(lm(standard_041$rfu_value~standard_041$standard_conc), DETECTR_041$rfu_value)
DETECTR_041 <- read.csv("../tidy_data/DETECTR_041_kinetics_tidy_metadata.csv")

samples_040 <- subset(DETECTR_041, DETECTR_041$time=="00:50:00" & DETECTR_041$kit %in% c("water"))

#samples_040 <- samples_040 %>% group_by(gRNA, reporter, target) %>% summarize (mean_rfu_value = mean(rfu_value), sd_rfu_value = sd(rfu_value), mean_amp = mean(AMP), sd_amp = sd(AMP))

ggplot(samples_040, aes(x = column_384, y = rfu_value, color = row_384)) +
  #facet_wrap(~sample_set)+
  geom_line(stat = 'identity') +
  geom_point(stat = 'identity') +

  scale_y_continuous(expand = c(0,0))+
  scale_x_continuous(breaks = seq(0,24,2))+

  ggtitle("DETECTR 041\nWaters plotted by column and colored by row")+
  scale_color_manual(values = c("darkslategray3", "mediumpurple3","darkseagreen3","olivedrab4","orange","yellow","blue","red","green","brown","black","purple","olivedrab2","grey","pink","orchid3"))+
  ylab("rfu_value") +
  xlab("row")+
  theme(axis.text.x = element_text(angle = 60, hjust = 1), 
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey"),
        panel.border = element_rect(fill = NA, color = "black"),
        title = element_text(face = "bold"),
        strip.background = element_rect(fill = NA, color = "black"),
        strip.text = element_text(size = 10),
        legend.title = element_blank()
          
        
)
```

## Kinetics over time, UMP and AMP

### Conclusions
AMP has exponential decay, while UMP has a more linear decay. All have a delayed peak in signal.

```{r echo=FALSE, warning=FALSE}

DETECTR_041 <- read.csv("../tidy_data/DETECTR_041_kinetics_tidy_metadata.csv")
DETECTR_041$standard_conc <- as.numeric(as.character(DETECTR_041$standard_conc))
DETECTR_041 <- subset(DETECTR_041,  DETECTR_041$sample_set %in% c("AMP_standard","UMP_standard"))
DETECTR_041$standard_conc <- factor(DETECTR_041$standard_conc)

ggplot(DETECTR_041, aes(x = time, y = rfu_value, color = standard_conc)) +
  facet_wrap(~sample_set, scale = "free_y")+
  #geom_line(stat = 'identity') +
  geom_point(stat = 'identity', size = 0.5) +
  scale_y_continuous(expand = c(0,0))+
 # scale_x_continuous(breaks = seq(0,24,2))+
  scale_color_manual(name = "concentration (uM)",values = c("darkslategray3", "mediumpurple3","darkseagreen3","olivedrab4","orange","yellow","blue","red","green","brown","black","purple","olivedrab2","grey","pink","orchid3"))+
  ylab("rfu_value") +
  xlab("time from 0 hr to 12 hr")+
  theme(axis.text.x = element_blank(), 
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey"),
        panel.border = element_rect(fill = NA, color = "black"),
        title = element_text(face = "bold"),
        strip.background = element_rect(fill = NA, color = "black"),
        strip.text = element_text(size = 10)
          
        
)

ggsave("DETECTR_041_AMP_UMP_Standards_Kinetic_Plot.pdf", width = 10, height = 6)
```

## Kinetics over time, UMP and AMP lower concentrations

### Conclusions
Lower concentration samples peak later than higher concentration samples and appear to have a linear decay.

```{r echo=FALSE, warning=FALSE}
DETECTR_041 <- read.csv("../tidy_data/DETECTR_041_kinetics_tidy_metadata.csv")
DETECTR_041$standard_conc <- as.numeric(as.character(DETECTR_041$standard_conc))

DETECTR_041 <- subset(DETECTR_041,  DETECTR_041$standard_conc < 0.2)
DETECTR_041$standard_conc <- factor(DETECTR_041$standard_conc)

ggplot(DETECTR_041, aes(x = time, y = rfu_value, color = standard_conc)) +
  facet_wrap(~sample_set, scale = "free_y")+
  #geom_line(stat = 'identity') +
  geom_point(stat = 'identity', size = 0.5) +
  scale_y_continuous(expand = c(0,0))+
 # scale_x_continuous(breaks = seq(0,24,2))+
  scale_color_manual(values = c("darkslategray3", "mediumpurple3","darkseagreen3","olivedrab4","orange","yellow","blue","red","green","brown","black","purple","olivedrab2","grey","pink","orchid3"))+
  ylab("rfu_value") +
  xlab("time from 0 hr to 12 hr")+
  theme(axis.text.x = element_blank(), 
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey"),
        panel.border = element_rect(fill = NA, color = "black"),
        title = element_text(face = "bold"),
        strip.background = element_rect(fill = NA, color = "black"),
        strip.text = element_text(size = 10),
        legend.title = element_blank()
          
        
)
```

```{r echo=FALSE, warning=FALSE}
DETECTR_041 <- read.csv("../tidy_data/DETECTR_041_kinetics_tidy_metadata.csv")
DETECTR_041$standard_conc <- as.numeric(as.character(DETECTR_041$standard_conc))
DETECTR_041 <- subset(DETECTR_041,  DETECTR_041$sample_set %in% c("AMP_standard","UMP_standard"))

DETECTR_041$standard_conc <- factor(DETECTR_041$standard_conc)

DETECTR_041_summarize <- DETECTR_041 %>% group_by(standard_conc, sample_set, time) %>% summarize (mean_rfu_value = mean(rfu_value), sd_rfu_value = sd(rfu_value))


ggplot(DETECTR_041_summarize, aes(x = time, y = mean_rfu_value, color = standard_conc)) +
  facet_wrap(~sample_set, scale = "free_y")+
  #geom_line(stat = 'identity') +
  geom_point(stat = 'identity', size = 1) +
  geom_errorbar(aes(ymin=mean_rfu_value-sd_rfu_value, ymax=mean_rfu_value+sd_rfu_value), width=.05,
                 position=position_dodge(.9), color = "black")+
  scale_y_continuous(expand = c(0,0))+
 # scale_x_continuous(breaks = seq(0,24,2))+
  scale_color_manual(name = "concentration (uM)",values = c("darkslategray3", "mediumpurple3","darkseagreen3","olivedrab4","orange","yellow","blue","red","green","brown","black","purple","olivedrab2","grey","pink","orchid3"))+
  ylab("rfu_value") +
  xlab("time from 0 hr to 12 hr")+
  theme(axis.text.x = element_blank(), 
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey"),
        panel.border = element_rect(fill = NA, color = "black"),
        title = element_text(face = "bold"),
        strip.background = element_rect(fill = NA, color = "black"),
        strip.text = element_text(size = 10),
        legend.title = element_blank()
          
        
)

ggsave("DETECTR_041_AMP_UMP_Standards_Kinetic_Plot_Means.pdf", width = 10, height = 6)


```