---
title: "DETECTR 033 Envision Overnight 384 Black Plate"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
library(dplyr)
library(data.table)
library(ggplot2)
```

```{r include=FALSE}
ggplotRegression <- function (fit) {

require(ggplot2)

ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5)#,
                     #"Intercept =",signif(fit$coef[[1]],5 ),
                     #" Slope =",signif(fit$coef[[2]], 5),
                     #" P =",signif(summary(fit)$coef[2,4], 5)
                     ))
}
```

```{r include=FALSE}

convertAMP <- function (fit, value) {

intercept = signif(fit$coef[[1]],5 )
slope = signif(fit$coef[[2]], 5)
AMP = (value - intercept)/slope


return(AMP)
}
```

```{r include=FALSE}
sumBelowTime <- function (DETECTR, hour) {

DETECTR = subset(DETECTR, plate_repeat < round(hour*60/7))
DETECTR_sum = DETECTR %>% group_by(Concentration_uM, NEBuffer, row_384,column_384) %>% summarize (total_rfu=sum(rfu_value))
return(DETECTR_sum)
}
```

```{r include=FALSE}
filterConcentration <- function (DETECTR, conc) {

DETECTR = subset(DETECTR, "Concentration (uM)" <= conc )

return(DETECTR)
}
```


## NEBuffer 4+ 2.1 Fresh Standard Curves for concentrations from 0.01uM to 10uM, including 0uM
+ 0hr (plate repeat 1) and 1hr (plate repeat 9) single time points are first two plots
+ Summation of all data points below 1hr (9), 3hr (26), 6hr (51) and 11.5hr (99) are next four plots

### Conclusion 
For all samples, summing up all rfu values that came before a certain timepoint gives no noticeable gains on the R2 value. There is significant difference between the replicates. 10uM doesn't seem out of the linear range on the Envision.

```{r DETECTR 033 all concentrations, echo=FALSE}

#every 7 mins for 99 total repeats
DETECTR_033 <- read.csv("../tidy_data/DETECTR_033_kinetics_tidy_metadata.csv")
DETECTR_033 <- subset(DETECTR_033, DETECTR_033$NEBuffer %in% c("NEBuffer 4 + 2.1 (fresh)", "NEBuffer 4 (fresh)", "NEBuffer 4 (thawed)"))
DETECTR_033 <- subset(DETECTR_033, DETECTR_033$NEBuffer %in% c("NEBuffer 4 + 2.1 (fresh)"))

DETECTR_033$Concentration_uM <- as.numeric(as.character(DETECTR_033$Concentration_uM))

DETECTR_033_0hr_single_point = subset(DETECTR_033,plate_repeat == 1)
DETECTR_033_1hr_single_point = subset(DETECTR_033,plate_repeat == round(60/7))
#DETECTR_033_30min = sumBelowTime(DETECTR_033,0,30,0)

DETECTR_033_1hr = sumBelowTime(DETECTR_033,1)
DETECTR_033_3hr = sumBelowTime(DETECTR_033,3)
DETECTR_033_6hr = sumBelowTime(DETECTR_033,6)
DETECTR_033_11.5hr = sumBelowTime(DETECTR_033,11.5)
ggplotRegression(lm(DETECTR_033_0hr_single_point$rfu_value~DETECTR_033_0hr_single_point$Concentration_uM))

ggplotRegression(lm(DETECTR_033_1hr_single_point$rfu_value~DETECTR_033_1hr_single_point$Concentration_uM))

#ggplotRegression(lm(DETECTR_033_30min$total_rfu~DETECTR_033_30min$Concentration_uM))

ggplotRegression(lm(DETECTR_033_1hr$total_rfu~DETECTR_033_1hr$Concentration_uM)) 
ggplotRegression(lm(DETECTR_033_3hr$total_rfu~DETECTR_033_3hr$Concentration_uM))
ggplotRegression(lm(DETECTR_033_6hr$total_rfu~DETECTR_033_6hr$Concentration_uM))

ggplotRegression(lm(DETECTR_033_11.5hr$total_rfu~DETECTR_033_11.5hr$Concentration_uM))


```



## NEBuffer 4+ 2.1 Fresh Standard Curves for concentrations from 0.01uM to 0.625uM, including 0uM
+ 0hr (plate repeat 1) and 1hr (plate repeat 9) single time points are first two plots
+ Summation of all data points below 1hr (9), 3hr (26), 6hr (51) and 11.5hr (99) are next four plots

### Conclusion 
For lower concentration samples, summing up all rfu values that came before a certain timepoint gives no noticeable gains on the R2 value. Hard to tell if Envision is more sensitive than SpectraMax.

```{r DETECTR 033 low concentrations, echo=FALSE}



#every 7 mins for 99 total repeats
DETECTR_033 <- read.csv("../tidy_data/DETECTR_033_kinetics_tidy_metadata.csv")
DETECTR_033 <- subset(DETECTR_033, DETECTR_033$NEBuffer %in% c("NEBuffer 4 + 2.1 (fresh)", "NEBuffer 4 (fresh)", "NEBuffer 4 (thawed)"))
DETECTR_033 <- subset(DETECTR_033, DETECTR_033$NEBuffer %in% c("NEBuffer 4 + 2.1 (fresh)"))
DETECTR_033 = subset(DETECTR_033,Concentration_uM<=1)


DETECTR_033$Concentration_uM <- as.numeric(as.character(DETECTR_033$Concentration_uM))

DETECTR_033_0hr_single_point = subset(DETECTR_033,plate_repeat == 1)
DETECTR_033_1hr_single_point = subset(DETECTR_033,plate_repeat == round(60/7))
#DETECTR_033_30min = sumBelowTime(DETECTR_033,0,30,0)

DETECTR_033_1hr = sumBelowTime(DETECTR_033,1)
DETECTR_033_3hr = sumBelowTime(DETECTR_033,3)
DETECTR_033_6hr = sumBelowTime(DETECTR_033,6)
DETECTR_033_11.5hr = sumBelowTime(DETECTR_033,11.5)
ggplotRegression(lm(DETECTR_033_0hr_single_point$rfu_value~DETECTR_033_0hr_single_point$Concentration_uM))

ggplotRegression(lm(DETECTR_033_1hr_single_point$rfu_value~DETECTR_033_1hr_single_point$Concentration_uM))

#ggplotRegression(lm(DETECTR_033_30min$total_rfu~DETECTR_033_30min$Concentration_uM))

ggplotRegression(lm(DETECTR_033_1hr$total_rfu~DETECTR_033_1hr$Concentration_uM)) 
ggplotRegression(lm(DETECTR_033_3hr$total_rfu~DETECTR_033_3hr$Concentration_uM))
ggplotRegression(lm(DETECTR_033_6hr$total_rfu~DETECTR_033_6hr$Concentration_uM))

ggplotRegression(lm(DETECTR_033_11.5hr$total_rfu~DETECTR_033_11.5hr$Concentration_uM))



```

## Buffer comparision at 1hr timepoint, with all concentrations and low concentrations
+ First three plots are all concentrations (NEBuffer 4+ 2.1 fresh, NEBuffer 4 fresh and NEBuffer 4 thawed)
+ Next three plots are low concentrations (NEBuffer 4+ 2.1 fresh, NEBuffer 4 fresh and NEBuffer 4 thawed)

### Conclusions
Not much difference between thawed and fresh. There may be something in NEBuffer2.1 that seems to improve the sensitivity at lower concentrations - R2 is much better in that buffer <0.625uM than with other buffers.

```{r DETECTR 033 buffer tests, echo=FALSE}

#every 7 mins for 99 total repeats
#all concentrations

DETECTR_033 <- read.csv("../tidy_data/DETECTR_033_kinetics_tidy_metadata.csv")
DETECTR_033$Concentration_uM <- as.numeric(as.character(DETECTR_033$Concentration_uM))
DETECTR_033 <- subset(DETECTR_033, DETECTR_033$NEBuffer %in% c("NEBuffer 4 + 2.1 (fresh)"))
DETECTR_033_1hr_single_point_NEBuffer4_2.1_Fresh = subset(DETECTR_033,plate_repeat == round(60/7))
#DETECTR_033_1hr_NEBuffer4_2.1_Fresh = sumBelowTime(DETECTR_033,1)
ggplotRegression(lm(DETECTR_033_1hr_single_point_NEBuffer4_2.1_Fresh$rfu_value~DETECTR_033_1hr_single_point_NEBuffer4_2.1_Fresh$Concentration_uM))
#ggplotRegression(lm(DETECTR_033_1hr_NEBuffer4_2.1_Fresh$total_rfu~DETECTR_033_1hr_NEBuffer4_2.1_Fresh$Concentration_uM))

DETECTR_033 <- read.csv("../tidy_data/DETECTR_033_kinetics_tidy_metadata.csv")
DETECTR_033$Concentration_uM <- as.numeric(as.character(DETECTR_033$Concentration_uM))

DETECTR_033 <- subset(DETECTR_033, DETECTR_033$NEBuffer %in% c("NEBuffer 4 + 2.1 (fresh)", "NEBuffer 4 (fresh)", "NEBuffer 4 (thawed)"))
DETECTR_033 <- subset(DETECTR_033, DETECTR_033$NEBuffer %in% c("NEBuffer 4 (fresh)"))
DETECTR_033_1hr_single_point_NEBuffer4_Fresh = subset(DETECTR_033,plate_repeat == round(60/7))
#DETECTR_033_1hr_NEBuffer4_Fresh = sumBelowTime(DETECTR_033,1)
ggplotRegression(lm(DETECTR_033_1hr_single_point_NEBuffer4_Fresh$rfu_value~DETECTR_033_1hr_single_point_NEBuffer4_Fresh$Concentration_uM))
#ggplotRegression(lm(DETECTR_033_1hr_NEBuffer4_Fresh$total_rfu~DETECTR_033_1hr_NEBuffer4_Fresh$Concentration_uM))

DETECTR_033 <- read.csv("../tidy_data/DETECTR_033_kinetics_tidy_metadata.csv")
DETECTR_033$Concentration_uM <- as.numeric(as.character(DETECTR_033$Concentration_uM))

DETECTR_033 <- subset(DETECTR_033, DETECTR_033$NEBuffer %in% c("NEBuffer 4 + 2.1 (fresh)", "NEBuffer 4 (fresh)", "NEBuffer 4 (thawed)"))
DETECTR_033 <- subset(DETECTR_033, DETECTR_033$NEBuffer %in% c("NEBuffer 4 (thawed)"))
DETECTR_033_1hr_single_point_NEBuffer4_Thawed = subset(DETECTR_033,plate_repeat == round(60/7))
#DETECTR_033_1hr_NEBuffer4_Thawed = sumBelowTime(DETECTR_033,1)
ggplotRegression(lm(DETECTR_033_1hr_single_point_NEBuffer4_Thawed$rfu_value~DETECTR_033_1hr_single_point_NEBuffer4_Thawed$Concentration_uM))
#ggplotRegression(lm(DETECTR_033_1hr_NEBuffer4_Thawed$total_rfu~DETECTR_033_1hr_NEBuffer4_Thawed$Concentration_uM))


#low concentrations

DETECTR_033 <- read.csv("../tidy_data/DETECTR_033_kinetics_tidy_metadata.csv")
DETECTR_033 = subset(DETECTR_033,Concentration_uM<=1)

DETECTR_033$Concentration_uM <- as.numeric(as.character(DETECTR_033$Concentration_uM))
DETECTR_033 <- subset(DETECTR_033, DETECTR_033$NEBuffer %in% c("NEBuffer 4 + 2.1 (fresh)"))
DETECTR_033_1hr_single_point_NEBuffer4_2.1_Fresh = subset(DETECTR_033,plate_repeat == round(60/7))
#DETECTR_033_1hr_NEBuffer4_2.1_Fresh = sumBelowTime(DETECTR_033,1)
ggplotRegression(lm(DETECTR_033_1hr_single_point_NEBuffer4_2.1_Fresh$rfu_value~DETECTR_033_1hr_single_point_NEBuffer4_2.1_Fresh$Concentration_uM))
#ggplotRegression(lm(DETECTR_033_1hr_NEBuffer4_2.1_Fresh$total_rfu~DETECTR_033_1hr_NEBuffer4_2.1_Fresh$Concentration_uM))

DETECTR_033 <- read.csv("../tidy_data/DETECTR_033_kinetics_tidy_metadata.csv")
DETECTR_033 = subset(DETECTR_033,Concentration_uM<=1)

DETECTR_033$Concentration_uM <- as.numeric(as.character(DETECTR_033$Concentration_uM))

DETECTR_033 <- subset(DETECTR_033, DETECTR_033$NEBuffer %in% c("NEBuffer 4 + 2.1 (fresh)", "NEBuffer 4 (fresh)", "NEBuffer 4 (thawed)"))
DETECTR_033 <- subset(DETECTR_033, DETECTR_033$NEBuffer %in% c("NEBuffer 4 (fresh)"))
DETECTR_033_1hr_single_point_NEBuffer4_Fresh = subset(DETECTR_033,plate_repeat == round(60/7))
#DETECTR_033_1hr_NEBuffer4_Fresh = sumBelowTime(DETECTR_033,1)
ggplotRegression(lm(DETECTR_033_1hr_single_point_NEBuffer4_Fresh$rfu_value~DETECTR_033_1hr_single_point_NEBuffer4_Fresh$Concentration_uM))
#ggplotRegression(lm(DETECTR_033_1hr_NEBuffer4_Fresh$total_rfu~DETECTR_033_1hr_NEBuffer4_Fresh$Concentration_uM))

DETECTR_033 <- read.csv("../tidy_data/DETECTR_033_kinetics_tidy_metadata.csv")
DETECTR_033 = subset(DETECTR_033,Concentration_uM<=1)

DETECTR_033$Concentration_uM <- as.numeric(as.character(DETECTR_033$Concentration_uM))

DETECTR_033 <- subset(DETECTR_033, DETECTR_033$NEBuffer %in% c("NEBuffer 4 + 2.1 (fresh)", "NEBuffer 4 (fresh)", "NEBuffer 4 (thawed)"))
DETECTR_033 <- subset(DETECTR_033, DETECTR_033$NEBuffer %in% c("NEBuffer 4 (thawed)"))
DETECTR_033_1hr_single_point_NEBuffer4_Thawed = subset(DETECTR_033,plate_repeat == round(60/7))
#DETECTR_033_1hr_NEBuffer4_Thawed = sumBelowTime(DETECTR_033,1)
ggplotRegression(lm(DETECTR_033_1hr_single_point_NEBuffer4_Thawed$rfu_value~DETECTR_033_1hr_single_point_NEBuffer4_Thawed$Concentration_uM))
#ggplotRegression(lm(DETECTR_033_1hr_NEBuffer4_Thawed$total_rfu~DETECTR_033_1hr_NEBuffer4_Thawed$Concentration_uM))



```

